Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-13 ijar-npb-ms.tex
text block for intro referring to a recent paper

>>>>

*** prior-data conflict: more cautious probability statements
(the reliability function is a collection of probability statements)

*** Prior-data conflict has recently also been considered by \citet{2015:bickel},
who, starting from a large class of reasonable models
(which could be seen as stemming from a near-noninformative set of priors),
identifies a subset of adequate models,
selected according to a model adequacy measure that rejects a prior if it leads to prior-data conflict.

 proposes a different approach
